---
title: "Geometric Object"
format: pdf
editor: visual
---

# Geometric Objects

-   Geometric objects or *geoms* are objects used to represent data.

-   I can represent data with point geom:

```{r}
#| message: false
#| warning: false
library(tidyverse)
ggplot(data = mpg) +
  geom_point(
    mapping = aes(x = displ, y = hwy, alpha = displ), #putting some color grading just for aesthetics
    show.legend = FALSE #removing the color grading legend since the x axis already do the job! 
  )

```

-   Or I can use a smooth line adjusted to the data:

    ```{r}
    #| message: false
    #| warning: false
    ggplot(data = mpg) +
      geom_smooth(
        mapping = aes(x = displ, y = hwy)
      )

    ```

-   I can also do *scaling* with the type of *smooth line*:

```{r}
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, linetype = drv, color = drv)
  )

```

-   It's also possible to combine different geoms:

    ```{r}
    #| message: false
    #| warning: false
    ggplot(data = mpg) +
      geom_smooth(
        mapping = aes(x = displ, y = hwy, linetype = drv, color = drv)
      ) +
      geom_point(
        mapping = aes(x = displ, y = hwy, alpha = drv)
      )
    ```

-   Nevertheless, it's possible to declare the variables directly in the `ggplot` function to use it in every geom, needing only to declare the variables you want in specific geoms:

    ```{r}
    #| message: false
    #| warning: false
    ggplot(data = mpg, mapping = aes( x = displ, y = hwy)) +
      geom_point(mapping = aes(color = class)) + 
      geom_smooth() #it will use the variables I declared in ggplot

    ```

-   Additionally, I can use the smooth line only to a subgroup of my data:

    ```{r}
    #| message: false
    #| warning: false
    ggplot(data = mpg, mapping = aes( x = displ, y = hwy)) +
      geom_point(mapping = aes(color = class)) + 
      geom_smooth(
        data = filter(mpg, class == "subcompact"), #filtering the smooth geom to the subgroup
        se = FALSE #removing the buffer around the line
      )

    ```
